A meta-analysis of mental rotation ability in the first years of life

### 2022-05-03 code/analysis.Rmd
Add table for frequentist results

# Meta-regression with gender, age, and task
res_reg <- rma.mv(
  gi, vi,
  mods = ~ gender * age_c + task,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_reg)
# forest(res_full)
```

>>>>

# Meta-regression with gender, age, and task
res_reg <- rma.mv(
  gi, vi,
  mods = ~ gender * age_c + task,
  random = ~ 1 | article / experiment,
  data = dat,
  slab = experiment
)
print(res_reg)
# forest(res_full)

# Extract standard deviations and ICCs
vars_ml <- list(matrix())

# Export results as a table
map2_dfr(
  c("Meta-analysis", "Meta-regression"),
  list(res_ml, res_reg),
  function(name, res) {
    # Intercept / regression weights
    tibble(
      Model = c(name, rep(NA, length(res$b) - 1)),
      Parameter = rownames(res$b),
      Estimate = print_num(as.numeric(res$b)),
      SE = print_num(res$se),
      z = print_num(res$zval),
      p = print_num(res$pval, digits = 3),
      ci_lower = print_num(res$ci.lb),
      ci_upper = print_num(res$ci.ub)
    ) %>%
      # Re-format confidence interval
      mutate(
        `95% CI` = str_c("[", ci_lower, ", ", ci_upper, "]"),
        .keep = "unused"
      ) %>%
      # Add variances
      bind_rows(tibble(
        Parameter = res$s.name,
        Estimate = print_num(res$sigma2)
      ))
  }
) %>%
  mutate(
    Parameter = c(
      "Hedges' g",
      "s2article",
      "s2experiment",
      "Intercept",
      "Female - mixed",
      "Male - female",
      "Age (per year)",
      "Habituation - VoE",
      "(Female - mixed) × age",
      "(Male - female) × age",
      "s2article",
      "s2experiment"
    )
  ) -> tab_freq

# Save the table
write_csv(tab_freq, file = here(tables_dir, "frequentist_results.csv"), na = "")
```
